Estimating individual subjective values of emotion regulation strategies

### 2023-03-14 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{49} was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting took place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies were presented with a monetary reward.
Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1 € for strategy A or 1 € for strategy B''.
They decided by clicking the on-screen button of the respective option.
Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1 €, the other strategy was assigned the fixed value of 2 €.
After this, comparisons between strategies followed the original COG-ED paradigm\textsuperscript{29}.
Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1 € was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2 € reward was chosen).
The adjustment started at 0.50 € and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chose the strategy with the fixed 2 € reward, the other strategy's last value on display was 1.97 €, if they always choose the lower strategy, its last value was 0.03 €.
The sixth adjustment of 0.02 € was done during data analysis, based on the participants' decision in the last display of the pairing.
Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.

@@

\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02 € was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2 €.
Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

@@

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our \href{https://github.com/ChScheffel/CAD}{Github repository}.

@@

Data collection took place between 2022-08 and 2023-02.
A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
Of these, \(N=125\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of \(N=120\) participants (100 female ; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).

@@

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator}, and \emph{Levator} activity.
We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\)´, \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological respoindng, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator}, and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in \protect\hyperlink{SupplementEffectER}{supplementary material}.

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\); see figure~\ref{fig:FigSubjEffort}).
Post-hoc test showed significant higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).

@@

{[}\ldots{} WAHLVERHALTEN FEHLT NOCH \ldots{]}

@@

Individual SVs could be determined for 120 participants for all three ER strategies.
SVs ranged between 0.005 and 1.00.
In sum, \(n=\) 119 had a SVs of 1.0, indicating a clear preference for one ER strategy.
Absolute preferences for ER strategies were relatively equally distributed.
Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 36.

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was \(ICC=\) 0.19, indicating that level-2 predictor subject accounted for 19.10 percent of total variance.
The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy (\(BF10\) of the variable strategy: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
Our model explained 0.90 percent of variance and thus we assumed our model was overfitted due to including recoded strategy as random slope.
We therefore set a new model without the recoded strategy as random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
\]

The second model explained 0.41 percent of variance.
All results of the second model are in table~\ref{tab:TabMLMH5}.

@@

The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5 percent of variance in SVs.
Effort rating showed an effect size of \(f^{2}=\) 0.035.
The effect sizes of all other predictors were negligibly small (\(f^{2}< 0.01\)).

@@

To investigate the ecological validity of the subjective values of ER strategies we calculated, we looked to see if SVs were associated with the actual choice of participants in the choice block.
Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 120) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVchoice}).

@@

We then conducted a ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with \(R^{2}=\) 0.27.
The predictor SV of strategy distraction was found to contribute to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
Additionally, the predictor SV of strategy suppression was found to contribute to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
The estimated odds ration indicated that is more likely to later choose suppression, when SV of strategy suppression is higher.

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
We found neither a significant associations between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).

@@

We exploratory wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level 2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.

>>>>

Further psychological constructs were assessed but had no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being was assessed using the German version of the WHO-5 scale\textsuperscript{45,46}.
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{47--49} was used.
Habitual use of ER will was assessed using the German version of the Emotion Regulation Questionnaire (ERQ)\textsuperscript{9,50}.
Implicit theories of willpower in emotion control was assessed using the implicit theories questionnaire from Bernecker and Job\textsuperscript{51}.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{28,52} was used.
To assess self-control\textsuperscript{53}, sum scores of the German versions of the following questionnaires were used: the Self-Regulation Scale (SRS)\textsuperscript{54}, the Brief Self-Control Scale (BSCS)\textsuperscript{55,56}, and the Barratt Impulsiveness Scale (BIS-11)\textsuperscript{57,58}.
Attentional control were assessed using the Attentional Control Scale (ACS)\textsuperscript{59}.
For more detailed information on psychometric properties of the questionnaires, please see \protect\hyperlink{SupplementQuestionnaires}{supplementary material}.

@@

\emph{Part two: ER effort discounting.} In the second part, ER effort discounting took place.
The procedure of the discounting will follow the COG-ED paradigm by Westbrook et al.\textsuperscript{29} with a major change.
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs.~distancing, distraction vs.~suppression, and distancing vs.~suppression), each of the two strategies were presented with a monetary reward.
Because there is no strategy that is objectively more difficult, we added initial comparisons asking the participants to choose between ``1€ for strategy A or 1€ for strategy B''.
They decided by clicking the on-screen button of the respective option.
Each of the three strategy pairs were presented three times in total, in a randomized order and randomly assigned which strategy appeared on the left or right side of the screen.
For each pair, the strategy that was chosen at least two out of three times was assigned the flexible starting value of 1€, the other strategy was assigned the fixed value of 2€.
After this, comparisons between strategies followed the original COG-ED paradigm\textsuperscript{29}.
Each pairing was presented six consecutive times, and with each decision the reward of the strategy with the starting value of 1€ was either lowered (if this strategy was chosen) or raised (if the strategy with the fixed 2€ reward was chosen).
The adjustment started at 0.50€ and each was half the adjustment of the previous step, rounded to two digits after the decimal point.
If a participant always chose the strategy with the fixed 2€ reward, the other strategy's last value on display was 1.97€, if they always choose the lower strategy, its last value was 0.03€.
The sixth adjustment of 0.02€ was done during data analysis, based on the participants' decision in the last display of the pairing.
Participants were instructed to decide as realistically as possible by imagining that the monetary reward was actually available for choice.

@@

\emph{Subjective values of emotion regulation strategies.} For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing.
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

@@

The paradigm code, the R script for analysis, and the R Markdown file used to compile this document are available at \href{https://osf.io/vnj8x/}{osf.io/vnj8x/}.

\hypertarget{protocol-registration}{%
\subsection{Protocol registration}\label{protocol-registration}}

The Stage 1 Registered Report protocol has been approved and is available at \href{https://osf.io/d6sc9/}{osf.io/d6sc9/}.

@@

Data collection took place between 2022-08 and 2023-02.
A total of \(N=151\) participants completed the online survey and were invited to participate in the two lab sessions.
Of these, \(N=125\) participated in the first laboratory session\textsuperscript{34} and \(N=121\) completed the second laboratory session.
Of these, \(n=1\) person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of \(N=120\) participants (100 female; age: \(M=22.5\text{ }\pm\text{ }SD = 3.0\)).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording (\(n=1\)) and failure to record utility ratings (\(n=18\)).

@@

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, \emph{Corrugator} and \emph{Levator} activity.
We found a highly significant main effect of valence for subjective arousal (\(F(1, 119) = 399.95\), \(p < .001\), \(\hat{\eta}^2_G = .589\), 90\% CI \([.498, .659]\), \(\mathrm{BF}_{\textrm{10}} = 1.47 \times 10^{44}\)), \emph{Corrugator} activity (\(F(1, 117) = 27.73\), \(p < .001\), \(\hat{\eta}^2_G = .111\), 90\% CI \([.037, .206]\), \(\mathrm{BF}_{\textrm{10}} = 8.67 \times 10^{16}\)), and \emph{Levator} activity (\(F(1, 117) = 8.87\), \(p = .004\), \(\hat{\eta}^2_G = .039\), 90\% CI \([.002, .111]\), \(\mathrm{BF}_{\textrm{10}} = 188.72\)), indicating that negative pictures successfully evoked emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, \emph{Corrugator} and \emph{Levator} activity of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy for subjective arousal (\(F(2.71, 322.55) = 7.39\), \(p < .001\), \(\hat{\eta}^2_G = .015\), 90\% CI \([.000, .036]\), \(\mathrm{BF}_{\textrm{10}} = 0.21\)), \emph{Corrugator} activity (\(F(1.76, 206.02) = 13.70\), \(p < .001\), \(\hat{\eta}^2_G = .056\), 90\% CI \([.019, .094]\), \(\mathrm{BF}_{\textrm{10}} = 6.16 \times 10^{7}\)), and \emph{Levator} activity (\(F(1.54, 180.41) = 19.95\), \(p < .001\), \(\hat{\eta}^2_G = .089\), 90\% CI \([.043, .134]\), \(\mathrm{BF}_{\textrm{10}} = 3.22 \times 10^{17}\)), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \ref{tab:SupplEffectArousalReg} to \ref{tab:SupplEffectLevReg} and figures \ref{fig:SupplFigArousalReg} to \ref{fig:SupplFigLevReg} in the \protect\hyperlink{SupplementEffectER}{supplementary material}.

@@

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (\(F(2.92, 347.65) = 128.47\), \(p < .001\), \(\hat{\eta}^2_G = .327\), 90\% CI \([.261, .384]\), \(\mathrm{BF}_{\textrm{10}} = 1.84 \times 10^{37}\); see figure~\ref{fig:FigSubjEffort}).
Post-hoc test showed significantly higher subjective effort for distraction (\(t(357) = -17.92\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 3.61 \times 10^{30}\)), distancing (\(t(357) = -15.82\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.60 \times 10^{28}\)), and suppression (\(t(357) = -12.26\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.27 \times 10^{19}\)) compared to active viewing.
Moreover, we found significantly lower effort during suppression compared with distraction (\(t(357) = 5.66\), \(p_\mathrm{\scriptsize Tukey(4)} < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.61 \times 10^{6}\)) and distancing (\(t(357) = 3.55\), \(p_\mathrm{\scriptsize Tukey(4)} = .002\), \(\mathrm{BF}_{\textrm{10}} = 29.19\)).

@@

The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group\textsuperscript{22}.
Here, 45.40\% stated that they chose the strategy that was easiest for them to implement.
24.40\% stated they chose the strategy that was most effective and 11.80\% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in Table XX in \protect\hyperlink{SupplementReasonChoice}{supplementary material}.

@@

Individual SVs could be determined for 120 participants for all three ER strategies.
SVs ranged between 0.005 and 1.00.
In sum, \(n=\) 119 had one SV of 1.0, indicating a clear preference for one ER strategy.
Absolute preferences for ER strategies were relatively equally distributed.
Highest SV for distraction was reported by \(n=\) 41, for distancing by \(n=\) 36, and for suppression by \(n=\) 43.

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was \(ICC=\) 0.19, indicating that the level-2 predictor subject accounted for 19.10\% of total variance.
The preregistered model showed a correlation of \(r=\) 0.95 of the random effects subjects and recoded strategy (\(BF10\) of the variable strategy: \(\mathrm{BF}_{\textrm{10}} = \infty\)).
Our model explained 0.90\% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
\]

The second model explained 0.41\% of variance.
All results of the second model are in Table~\ref{tab:TabMLMH5}.

@@

The predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = -13.98\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,618.96) = 29.49\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,618.96) = 2.09\), \(p = .037\)) showed a significant association with SVs.
The values were relatively small, so the respective effect size \(f^{2}\) was calculated as the explained variance.
Interestingly, utility rating showed the greatest effect size of all predictors (\(f^{2}=\) 0.155), indicating that utility rating explained 15.5\% of variance in SVs.
Effort rating showed an effect size of \(f^{2}=\) 0.035.
The effect sizes of all other predictors were negligibly small (\(f^{2}< 0.01\)).

@@

To investigate the ecological validity of the subjective values of ER strategies we calculated, we tested whether SVs were associated with the actual choice of participants in the choice block.
Therefore, a \(\chi^{2}\) test with predicted choice (i.e., the strategy with the highest SV of each participant) and actual choice was computed.
There was a significant association between predicted choice and actual choice (\(\chi^2(4, n = 119) = 115.40\), \(p < .001\), \(\mathrm{BF}_{\textrm{10}} = 1.62 \times 10^{21}\); see figure~\ref{fig:FigSVChoice}).

@@

We then conducted an ordinal regression with the dependent variable ``choice'' and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with \(R^{2}=\) 0.27.
The predictor SV of strategy distraction was found to contribute to the model (\(b = -6.29\), 95\% CI \([-10.81, -3.02]\), \(z = -3.21\), \(p = .001\), \(BF10=\) 2.00).
The estimated odds ratio indicated a higher chance of choosing strategy distraction, when SV of that strategy is higher.
Additionally, the predictor SV of strategy suppression was found to contribute to the model (\(b = 2.70\), 95\% CI \([0.83, 4.84]\), \(z = 2.67\), \(p = .008\), \(BF10=\) 1.99).
The estimated odds ration indicated that a participant is more likely to later choose suppression, when SV of strategy suppression is higher.

Last, we investigated whether SVs are associated with ER flexibility.
We conducted a logistic regression to inspect whether participants' individual \(slopes\) and \(intercepts\) of ordered SVs could predict their ER flexibility score.
We found neither a significant association between \(slopes\) of SVs and FlexER score (\(b = -0.36\), 95\% CI \([-1.28, 0.56]\), \(t(117) = -0.77\), \(p = .444\), \(\mathrm{BF}_{\textrm{10}} = 0.72\)), nor between \(intercepts\) and FlexER score (\(b = 1.32\), 95\% CI \([-1.38, 4.02]\), \(t(117) = 0.97\), \(p = .336\), \(\mathrm{BF}_{\textrm{10}} = 0.85\)).
However, model fit was relatively low (\(R^2 = .03\), \(F(2, 117) = 1.93\), \(p = .150\)).

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before.
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
\[
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
\]
As one would expect, the predictors effort rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = -14.26\), \(p < .001\)), utility rating (\(\hat{\beta} = 0.00\), 95\% CI \([0.00, 0.00]\), \(t(5,620.93) = 33.28\), \(p < .001\)), and \emph{Corrugator} activity (\(\hat{\beta} = 0.01\), 95\% CI \([0.00, 0.01]\), \(t(5,620.93) = 2.12\), \(p = .034\)) showed a significant association with SVs.
In addition, a positive association was also found between self-control and SVs (\(\hat{\beta} = 0.02\), 95\% CI \([0.00, 0.05]\), \(t(97.97) = 2.04\), \(p = .044\)).
However, the effect size of self-control was negligibly small (\(f^{2}=\) 0.002).
Detailed information can be found in the \protect\hyperlink{SupplementExploratory}{supplementary material}.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The present Registered Report sought to evaluate whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies strategies distraction, distancing, and suppression.
We therefore adapted the Cognitive Effort Discounting Paradigm by Westbrook et al.\textsuperscript{29} in a way that allows to determine SVs for tasks that have no objective order of difficulty levels.
The new paradigm was tested on an \emph{n}-back task\textsuperscript{34} and a classic ER paradigm.
The latter was completed by \(N=120\) participants.
As expected, use of ER strategies was associated with decreased subjective and physiological arousal.
This finding is in line with previous meta-analytic findings, indicating the effectiveness of ER strategies, both on subjective as well as physiological levels\textsuperscript{4,5}.
Further, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing.
This allows us to replicate previous findings from our research group and show that the use of strategies is associated with cognitive effort\textsuperscript{22}.
Both measures also showed great variability between individuals.
Taken together, this means that the ER strategies had an effect on the participants as intended: Individuals were able to reduce subjective and physiological responding effectively at the expense of cognitive effort.
We assume that there was a good basis on which individual SVs of ER strategies could be determined.
All in all, evidence was in favour of hypotheses H1 to H5.

Almost all participants showed an absolute preference for one strategy, indicated by an SV of 1.
We also found a wide range of SVs (between 0.005 and 1.00), suggesting that individuals prefer strategies to different extents.
There was a significant relationship between SVs and choice of strategy.
Overly frequent the strategy would be chosen by the persons for whom the highest subjective value had been determined before, which speaks in favour of hypothesis H7.
Further, we found associations between individual SVs and different predictors.
Subjective effort, utility, and \emph{Corrugator} muscle activity significantly predicted individual SVs.
Contrary to our hypothesis H6, utility was the best predictor for individual SVs, explaining 15.5 percent of variance in SVs.
However, individual SVs did not show associations with ER flexibility, we therefore found no evidence for hypothesis H7.

\hypertarget{ecological-validity-of-subjective-values-of-er-strategies}{%
\subsection{Ecological validity of subjective values of ER strategies}\label{ecological-validity-of-subjective-values-of-er-strategies}}

Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy\textsuperscript{17,69,70}.
Greater variability might even adaptive\textsuperscript{12,17}.
In addition, a wide variety of factors that influence the choice of stratgies in specific situations were examined\textsuperscript{20--22,71,72}.
Thus, different factors have only rarely been studied together\textsuperscript{72}.
Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.\textsuperscript{21}) cannot be used to determine what internal subjective value the subjects associated with the strategies.
However, we succeeded in this with our new CAD paradigm.
On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
The highest SVs of the individuals were associated with the choice made by the participants.
Until now, it has been difficult to transfer such findings from the laboratory to everyday life\textsuperscript{71}.
This could be due to the fact that the strategies that have to be chosen between are often fixed in laboratory tests by the experimental design\textsuperscript{20--22}.
It was therefore attempted to investigate ER choice and influencing factors in everyday life.
However, even there, certain strategies were often prescribed (for example studies, see English et al.\textsuperscript{73}, Millgram et al.\textsuperscript{74}, Wilms et al.\textsuperscript{71}).
Although these covered a large area of the emotion-genesis process\textsuperscript{2}, they were nevertheless ultimately fixed.
Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
However, it would be possible to use ecological momentary assessment to capture ER strategies\textsuperscript{75}.
This would allow all strategies of the ER repertoire to be recorded for each individual\textsuperscript{12}.
Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination\textsuperscript{76}.

Dynamic processes in emotion regulation choice
Jonathan W. Murphy
\& Michael A. Young

\hypertarget{trait-character-of-svs}{%
\subsection{Trait character of SVs}\label{trait-character-of-svs}}

Hat das Trait-Charakter?

State character of goals\textsuperscript{71}

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

Our findings must be considered in light of several limitations.
First, it must be mentioned that a block design was used.
This allows for habituation effects of EMG activity within the block.
However, block designs are common in ER research\textsuperscript{77} and were used in previous studies\textsuperscript{78}.
Second, it has to be mentioned that subjective arousal, effort, and utility ratings were conducted retrospectively at the end of each block.
It is also known that affect labeling might attenuate emotional experience\textsuperscript{79,80}.
That is why we decided not to have the ratings done after every image.
Furthermore, we were able to confirm our manipulation checks, indicating that implementation of ER strategies was successful, both on subjective and physiological levels.
Taken together, these two facts may have led to slightly lower associations between SVs and predictors.

Third, it is a major limitation that participants had to use three given ER strategies.
It could be that some of the participants did not implement or were used to any of the three strategies in everyday life.
So it may be that none of the strategies has a really high subjective value for the person.
However, strategies for attentional deployment, cognitive change, and response modulation were chosen that meta-analytically proved to be most effective\textsuperscript{4}.
Related to that, individual SVs of each person have to be interpreted with caution.
They depend on the specific context: The stimulus material presented and the strategies that are compared with each other.
Thus, it could be that SVs for one ER strategy would be higher or lower when using other stimuli or valences of stimuli and other comparison strategies.
That is because the computation of SVs is inseparable form the other SVs.

Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
However, we chose this amount because, first, we have followed the original paradigm of Westbrook\textsuperscript{29}.
Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort\textsuperscript{81}.
n the future, however, it should be examined how the level of incentives affects subjective values.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}
